---
title: "Rayshader in the Ladakh area"
description: |
  Beautiful terrain in the Ladakh area...
author:
  - name: Pavitra Chakravarty
base_url: https://genomix.netlify.app/
output: 
  distill::distill_article:
    toc: true
    toc_depth: 3
    self_contained: false
categories:
  - rayshader
  - Derek Watkin
  - USGS Earth Explorer
  - GEBCO
preview: CopyOfpreview.png
twitter:
  site: "@genomixgmailcom"
  creator: "@genomixgmailcom"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(rvest)
library(tidyverse)
```

## Source Data

The data comes from [Wikipedia](https://en.wikipedia.org/wiki/List_of_most-streamed_songs_on_Spotify), specifically a list of the most streamed songs on Spotify. We can scrape the table into R w/ `rvest`.

```{r load packages, eval = FALSE}
library(rvest)
library(tidyverse)
```

Now that we have the libraries loaded, let's read in the data, pull in the top 100, and add some new columns to use across our charts.

```{r get data}
url <- "https://en.wikipedia.org/wiki/List_of_most-streamed_songs_on_Spotify"

df <- url %>% 
  read_html() %>% 
  html_table(fill = TRUE) %>% 
  .[[1]] %>% 
  set_names(nm = c("rank", "song_name", "artist", "album", "streams", "date_published")) %>% 
  slice(1:100) %>% 
  mutate(num_rank = parse_number(rank),
         streams_comma = streams,
         streams = parse_number(streams)/1000,
         streams_text = if_else(
           num_rank == 1,
           paste(round(streams, digits = 2), "billion streams"),
           as.character(round(streams, digits = 2))
           ),
         lab_text = glue::glue("{rank}. {song_name} by {artist}"),
  ) %>% 
  as_tibble()

df %>% glimpse()
```
<aside> Note that there is `\` in front of the song name and in the lab_text as there we have to escape the `"` in each of those strings. </aside>

Data is ready to go!


# Chart 1: Font-height bars

```{r fontheight bars}
font_height_bars <- df %>% 
    filter(num_rank <=10) %>
```
